From clusters to queries: exploiting uncertainty in the modularity landscape of complex networks

### 2018-05-01 article/article.tex
YAY

\author{James P Gilbert}
\affiliation{%
  \institution{Synthetic biology research centre}
  \streetaddress{University of Nottingham}
  \city{Nottingham}
  \country{United Kingdom}
  \postcode{NG7 2RD}
}
\email{james.gilbert@nottingham.ac.uk}

@@

    \begin{subfigure}[b]{0.48\textwidth}
        \centering
        \includegraphics[width=\textwidth]{images/rocs/arabidopsis_ppi.png}
        \caption{Arabidopsis PPI protein complexes}
    \end{subfigure}
    \begin{subfigure}[b]{0.48\textwidth}
        \centering
        \includegraphics[width=\textwidth]{images/rocs/arabidopsis_ppi_go_complexes.png}
        \caption{E coli PPI protein complexes}
    \end{subfigure}
    \caption{ROC scores for the high quality labels for real networks described in Section \ref{sec:real_network_descs}. 
    Results represent the averages over all label sets.
    Shaded areas indicate standard deviations.}
    \label{fig:quality_label_rocs}
\end{figure*}
% 
% 
\subsubsection{High quality labels}
In this section we observe the performance of our method on the real networks described in Section \ref{sec:real_network_descs} with high quality, gold standard, curated labels.
For the EU Emails dataset, the communities relate to real departments of individuals.
For the protein interaction datasets we used manually curated interaction sets.
In the case of the Yeast this was taken from experimentally validated complexes  \cite{pu2008up}.
For the \textit{E coli} dataset we used manually curated interacting proteins from \cite{}.
For the Arabidopsis dataset, the complex sources were more limited.
Consequently, the IntAct database was used with all protein complexes listed containing less than 10 proteins in total \cite{}.

@@

However, this approach requires the community landscape to contain many local maxima, a property likely shared by many real-world, heterogeneous networks.
Similarly, the method presented here requires both some labelled data and the labels to be represented well within the topology of the underlying network.
The approach presented here differs from other ensemble approaches in that the objective is to provide a probabilistic framework for label classification.
This approach performs extremely well on both synthetically generated networks and real-world ground truth communities with relatively small sets of labels.

This work presents a number of interesting potential future avenues for research, such as observing how query sets change in time dynamic or multi-scale networks.
Similarly, further analysis could be conducted to test how large the set of high value partitions needs to be, and how applicable this approach can be to very large graphs.

\section*{Acknowledgements}
We are grateful for access to the University of Nottingham High Performance Computing Facility for supporting this work.
This work was supported by the Biotechnology and Biological Sciences Research Council grant BB/L013940/1.

>>>>

\author{James P Gilbert}
\affiliation{%
  \institution{Synthetic Biology Research Centre}
  \streetaddress{University of Nottingham}
  \city{Nottingham}
  \country{United Kingdom}
  \postcode{NG7 2RD}
}
\email{james.gilbert@nottingham.ac.uk}

@@

    \begin{subfigure}[b]{0.48\textwidth}
        \centering
        \includegraphics[width=\textwidth]{images/rocs/arabidopsis_ppi.png}
        \caption{Arabidopsis PPI protein complexes}
    \end{subfigure}
    \begin{subfigure}[b]{0.48\textwidth}
        \centering
        \includegraphics[width=\textwidth]{images/rocs/ecoli_ppi.png}
        \caption{E coli PPI protein complexes}
    \end{subfigure}
    \caption{ROC scores for the high quality labels for real networks described in Section \ref{sec:real_network_descs}. 
    Results represent the averages over all reciever operating characteristic scores from all samples of label sets with the cross validation procedure described in \ref{sec:cross_validation}.
    Shaded areas indicate standard deviations.}
    \label{fig:quality_label_rocs}
\end{figure*}
% 
% 
\subsubsection{High quality labels}
In this section we observe the performance of our method on the real networks described in Section \ref{sec:real_network_descs} with high quality, gold standard, curated labels.
For the EU Emails dataset, the communities relate to real departments of individuals.
For the protein interaction datasets we used manually curated interaction sets.
In the case of the Yeast this was taken from experimentally validated complexes  \cite{pu2008up}.
For the \textit{E coli} dataset we used manually curated interacting proteins from \cite{}.
For the Arabidopsis dataset, the complex sources were more limited.
Consequently, the IntAct database was used with all protein complexes listed containing less than 10 proteins in total \cite{}.

@@

However, this approach requires the community landscape to contain many local maxima, a property likely shared by many real-world, heterogeneous networks.
Similarly, the method presented here requires both some labelled data and the labels to be represented well within the topology of the underlying network.
The approach presented here differs from other ensemble approaches in that the objective is to provide a probabilistic framework for label classification.
This approach performs extremely well on both synthetically generated networks and real-world ground truth communities with relatively small sets of labels.
However, in a practical application this would still require selecting some form of arbitrary cut off for defining \textit{crisp} communities.

This also work presents a number of interesting potential future avenues for research, such as observing how query sets change in time dynamic or multi-scale networks.

\section*{Acknowledgements}
We are grateful for access to the University of Nottingham High Performance Computing Facility for supporting this work.
This work was supported by the Biotechnology and Biological Sciences Research Council grant BB/L013940/1.
We would like to thank Nicole Pearcy for assistance with this manuscript.
